AIS

### 2023-04-19 02_AIS.Rmd
Added code for AIS pts within 10km buffer

library(tidyverse)
library(sf)
```

@@

# Need to add more AIS dates in data folder
AISlist <- list.files(path = paste0("data/"), pattern = "AIS_", recursive = TRUE)

for (v in AISlist) {
  Adata <- read_csv(paste0("data/", v), show_col_types = FALSE) %>%
    filter(Length >= 100) %>%                  # Filter out vessels over 100m in length
    dplyr::select(-SOG,-COG, -CallSign, -IMO, -Cargo, -Draft, -Status) %>%  #Remove unnecessary columns
    mutate(variable = paste0(substr(v, 16, 17), substr(v, 6, 7)))

@@

AIS_sf <- AIS %>%
  st_as_sf(coords = c("LON", "LAT"), crs=4326, remove=F)
```

@@

pois <- st_transform(trk8, crs = 4326)    # Specify a crs
pts_buff <- st_buffer(pois, dist = 10000)  # Buffer all points in trk to 10 km (10000m)
buff <- st_transform(pts_buff, crs = 4326)  # Specify crs for new buffer

@@

#Another way to view with TRUE/FALSE if AIS points fall within buffer
intersect <- st_intersects(buff, AIS_crop)
lgth <- lengths(st_intersects(buff, AIS_crop)) > 0

# Speeding up st_intersection (from https://github.com/r-spatial/sf/issues/801)

  st_intersection(x, y_subset,...)
}
inters <- st_intersection_faster(buff, AIS_crop[1:140,])
inters2 <- st_intersection_faster(buff, AIS_crop[141:200,])
inters3 <- st_intersection_faster(buff, AIS_crop[201:300,])

@@

# Plot showing AIS bounding box around drift 8 tracks
ggplot() + geom_sf(data = AIS_crop,color = "red")

>>>>

library(tidyverse)
library(sf)

# Function
# Speeding up st_intersection (from https://github.com/r-spatial/sf/issues/801)

  st_intersection(x, y_subset,...)
}
```

@@

# Need to add more AIS dates in data folder
AISlist <- list.files(path = paste0("data-raw/"), pattern = "AIS_", recursive = TRUE)

for (v in AISlist) {
  Adata <- read_csv(paste0("data-raw/", v), show_col_types = FALSE) %>%
    filter(Length >= 100) %>%                  # Filter out vessels over 100m in length
    dplyr::select(-SOG,-COG, -CallSign, -IMO, -Cargo, -Draft, -Status) %>%  #Remove unnecessary columns
    mutate(variable = paste0(substr(v, 16, 17), substr(v, 6, 7)))

@@

AIS_sf <- AIS_091218 %>%
  st_as_sf(coords = c("LON", "LAT"), crs=4326, remove=F)
```

@@

pois <- st_transform(trk8, crs = 4326)    # Specify a crs
pts_buff <- st_buffer(pois, dist = 10000)  # Creates 10 km buffer around buoy points 10 km (10000m)
buff <- st_transform(pts_buff, crs = 4326)  # Specify crs for new buffer

@@

#Another way to view AIS points that fall within buffer. DOES NOT consider time.
AIS_within_buff <- AIS_crop[buff,]
by <- join_by(closest(UTC >= BaseDateTime))
trk_AIS <- left_join(as.data.frame(trk8), as.data.frame(AIS_within_buff), by)

inters <- st_intersection_faster(buff, AIS_crop[1:140,])
inters2 <- st_intersection_faster(buff, AIS_crop[141:200,])
inters3 <- st_intersection_faster(buff, AIS_crop[201:300,])

@@

# Plot showing AIS bounding box around drift 8 tracks
ggplot() + geom_sf(data = trk_AIS, color = "red")
ggplot() + geom_sf(data = buff[lgth,] ,color = "red")
